### 2017-06-01 gpu-04-03-accelerator.tex
NVidia iso Nvidia, small rephrase

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Using OpenCL and CUDA}
%OpenCL/CUDA
Initially, the system was developed using OpenCL~\cite{opencl} in order to
accelerate the computations of the algorithm. OpenCL was chosen as it provides
a common abstraction for a variety of compute devices which fulfilled our
requirements of employing CPUs or GPUs. However, Nvidia's OpenCL SDK limits the
total memory allocations within a context to 4GB which severely limits the
problem sizes that can be tackled on GPUs. Therefore, we migrated the system to
use the abstraction layer CLCudaAPI~\cite{claduc}
to support both OpenCL and CUDA~\cite{Nickolls:2008:SPP:1365490.1365500}
as back-ends.
%
CLCudaAPI
hides the difference between OpenCL and the CUDA driver API.
For example, the library provides abstractions for Device, Context, Queue and
Buffer. Additionally, the implementations use a combination of inline functions
and preprocessor macros to abstract away the differences between OpenCL's and
CUDA's primitive types, address spaces and functions.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Using OpenCL and CUDA}
%OpenCL/CUDA
Initially, the system was developed using OpenCL~\cite{opencl} in order to
accelerate the computations of the algorithm. OpenCL was chosen as it provides
a common abstraction for a variety of compute devices which fulfilled our
requirements of employing CPUs or GPUs. However, NVidia's OpenCL SDK limits the
total memory allocations within a context to 4GB which severely limits the
problem sizes that can be tackled on GPUs. Therefore, we migrated the system to
use the abstraction layer CLCudaAPI~\cite{claduc}
to support both OpenCL and CUDA~\cite{Nickolls:2008:SPP:1365490.1365500}
as back-ends.
%
CLCudaAPI
hides the difference between OpenCL and the CUDA driver API.
For example, the library provides abstractions for Device, Context, Queue and
Buffer. Additionally, the implementations use a combination of inline functions
and preprocessor macros to abstract away the differences between OpenCL's and
CUDA's primitive types, address spaces and functions.

### 2017-06-01 gpu-05-evaluation.tex
NVidia iso Nvidia, small rephrase

The following sections provide a detailed experimental performance analysis
of the optimizations described above. We start by discussing the performance
effects of parallelizing the computations
on a multi-core CPU using OpenCL.
%
Next, we assess the trade-offs associated with each of the GPU optimization
strategies and their performance effects on four GPUs spanning two chip
architecture generations.
%
Finally, we present the overall outcome of accelerating the algorithm by
displaying its fast convergence over the largest networks that fit in the
memory of one GPU or CPU.

As noted in Section~\ref{sec-experimental}, all experiments were conducted on the VU Amsterdam DAS5 cluster.
Table~\ref{table-gpus} presents the properties of the various GPUs in
the DAS5 cluster.

>>>>

The following sections provide a detailed experimental performance analysis
of the optimizations described above. We start by discussing the performance
effects of parallelizing the computations
on a multi-core CPU using OpenCL.
%
Next, we assess the trade-offs associated with each of the GPU optimization
strategies and their performance effects on five GPUs spanning three chip
architecture generations.
%
Finally, we present the overall outcome of accelerating the algorithm by
displaying its fast convergence over the largest networks that fit in the
memory of one GPU or CPU.

\input{04-experimental-setup}

% As noted in Section~\ref{sec-experimental}, all experiments were conducted on the VU Amsterdam DAS5 cluster.
% Table~\ref{table-gpus} presents the properties of the various GPUs in
% the DAS5 cluster.
